{fairmetrics}: An R package for group fairness evaluation

### 2025-05-30 paper.Rmd
Add one comment.

Should the user wish to calculate an individual metric, it is possible to use any of the `eval_*` functions. For example, to calculate the equal opportunity metric, the user can call the `eval_equal_opportunity()` function.

@@

For group-specific performance metrics, such as the True Positive Rate (TPR), False Positive Rate (FPR), Positive Predictive Value (PPV), Negative Predictive Value (NPV), and others, the `get_all_metrics()` function can be used. This function returns a data frame with the metrics calculated for each group. [ NOTE: To me it is unclear why this is a separate function.  I think instead it makes sense to have an argument in your get_fairness_metrics function that turns the CI calculation on or off.  ]

>>>>

Should the user wish to calculate an individual criteria, it is possible to use any of the `eval_*` functions. For example, to calculate equal opportunity, the user can call the `eval_equal_opportunity()` function.

@@

For group-specific performance metrics, such as the True Positive Rate (TPR), False Positive Rate (FPR), Positive Predictive Value (PPV), Negative Predictive Value (NPV), and others, the `get_all_metrics()` function can be used. This function returns a data frame with the metrics calculated for each group.

[ NOTE: To me it is unclear why this is a separate function.  I think instead it makes sense to have an argument in your get_fairness_metrics function that turns the CI calculation on or off.  ]
